Nanophotonic Computational Design

### 2013-03-27 defense/intel.tex
Added intel stuff.

\title{Nanophotonic Computational Design}
\author{Jesse Lu}
\MyLogo{Jesse Lu PhD defense, Jelena Vuckovic group, Stanford University}
\date{February 25, 2013}

@@

\I  Full-parameter design must be \emph{design-by-description}
\pause
\begin{verbatim}
\\ Human describe here.
device mux2 
    in: {freq1, freq2}
    out1 <= freq1
    out2 <= freq2
\end{verbatim}
\pause
\smallfig{thesolution}
\nextpage

\I  \bold{Realization}: Design-by-description is \emph{extremely powerful}
\pause
    \BI The description (or function) of all useful devices is known
    \I  Therefore, design-by-description enables the design of \emph{everything} 
    \EI
\pause
\I  Also, does not require nanophotonic expertise
\pause
\I  \bold{Assumption}: Design-by-description can actually be made to work
\pause
\I  \bold{Our goal}: Make it work!

@@

\oursection{Summary}
\smallfig{takeaway}
\I  Designed 3D linear nanophotonic devices
    \BI Using the full parameter space
    \I  Using design-by-description \EI
\nextpage

@@

\oursection{Final result: Design of 3D linear nanophotonic devices}
\I  Finally, enough understanding to tackle the \emph{real} design problem
\pause
\I  \bold{Goal}: Software to design \emph{all} linear nanophotonic devices
\pause
    \BI Design-by-description (objective-first)
    \I  Uses the full parameter space
    \I  High efficiency
    \I  Fully three-dimensional (no approximations)
    \I  Multi-mode
    \I  Discrete, planar, manufacturable structure \EI
\nextpage

@@

\oursection{Result 1: Mode converter (TE)}
\threeDfig{3Db_wgc_te}
% \I  Converts from fundamental TE (in-plane polarized) mode to 
%     second-order mode
\I  Performance description at output waveguide:
    \BI Power in second-order mode: 90\% to 100\%
    \I  Power in first-order mode: 0\% to 1\% (rejection) \EI
\nextpage

@@

\I  Efficiency: 88.6\%, 90.6\%, 87.3\%
\bigfig{hub_3x3}
\I  Rejection modes no longer used for computational efficiency 
\newpage

@@

\oursection{Result 11: Wavelength-splitting fiber coupler}
\threeDfig{3Db_fib_wdm}
\I  A fusion of result 9 (fiber coupler) and result 5 (wavelength splitter)
\I  Shows the power of full-parameter design-by-description
\nextpage

@@

\oursection{Results summary}
\stepwise{
\I  Variety of devices suggests all devices possible
    \BI Converters: both TE and TM polarizations
    \I  Splitters: spatial, polarization, wavelength
    \I  Hubs: 3x3, 4x4, 2x2x2
    \I  Fiber couplers: compact, mode-splitting, wavelength-splitting \EI
\step{
\I  Design-by-description is a key enabler
    \BI All 11 final results achieved in only 3 weeks
    \I  Of course, 7 years of development and 18 months of programming\ldots \EI
}
\step{
\I  Individual design runtimes between 8-80 hours
    \BI Many future speedups possible at all levels \EI
}}

@@

\oursection{Conclusion}
\footnotetext{$^\ast$maybe}
\I  How to design any$^\ast$ linear multi-mode nanophotonic device
    \BI using the full parameter space
    \I  simply by describing its operation \EI
\pause
\I  Our method results in designs which are
    \BI extremely compact
    \I  manufacturable \EI
\pause
\I  Devices can be designed which are robust to
    \BI wavelength and temperature shifts 
    \I  fabrication error \EI
\oursection{Acknowledgements}
\begin{quote}
Not unto us, O Lord, not unto us, \\
But to Your name give glory, \\
Because of Your mercy, \\
Because of Your truth. (Psalm 115:1)
\end{quote}
\stepwise{
\step{Mom, Dad, }
\step{Jennifer, }
\step{Eli, }
\step{Seth, Lieven, Kelley,}
\step{Shanhui, Mark,}
\step{David,}
\step{Jelena,}
\step{Stephen,}
\step{Maria, Yiyang, Szu-lin, Gary,}
\step{JVgroup,}
\step{Owen, Paul,}
\step{Wonseok,}
\step{Ingrid,}
\step{Church family,}
\step{Sandy, Josiah}

\step{\begin{center}Thank you\end{center}}
}
\EI
\end{document}

>>>>

\title{Nanophotonic Computational Design}
\author{Jesse Lu}
\MyLogo{Jesse Lu, Jelena Vuckovic group, Stanford University}
\date{March 29, 2013}

@@

\I  Full-parameter design must be \emph{design-by-specification}
\pause
\begin{verbatim}
\\ Human specifiy performance here.
device mux2 
    in: {freq1, freq2}
    out1 <= freq1
    out2 <= freq2
\end{verbatim}
\pause
\smallfig{thesolution}
\nextpage

\I  \bold{Realization}: Design-by-specification is \emph{extremely powerful}
\pause
    \BI The specification (or function) of all useful devices is known
    \I  Therefore, design-by-specification enables the design of \emph{everything} 
    \EI
\pause
\smallfig{profs}
\I  \bold{Approach}: Apply basic optimization concepts to nanophotonic design

@@

\oursection{Summary}
\smallfig{takeaway}
\I  Designed 3D linear nanophotonic devices
    \BI Using the full parameter space
    \I  Using design-by-specification\EI
\nextpage

@@

\oursection{Final result: Design of 3D linear nanophotonic devices}
\I  Finally, enough understanding to tackle the \emph{real} design problem
\pause
\I  \bold{Goal}: Software to design \emph{all} linear nanophotonic devices
\pause
    \BI Design-by-specification (objective-first)
    \I  Uses the full parameter space
    \I  High efficiency
    \I  Fully three-dimensional (no approximations)
    \I  Multi-mode
    \I  Discrete, planar, manufacturable structure \EI
\nextpage

@@

\oursection{Result 1: Mode converter (TE)}
\threeDfig{3Db_wgc_te}
% \I  Converts from fundamental TE (in-plane polarized) mode to 
%     second-order mode
\I  Performance specification at output waveguide:
    \BI Power in second-order mode: 90\% to 100\%
    \I  Power in first-order mode: 0\% to 1\% (rejection) \EI
\nextpage

@@

\I  Efficiency: 88.6\%, 90.6\%, 87.3\% (Rejection modes no longer used)
\bigfig{hub_3x3}
\newpage

@@

\oursection{Result 11: Wavelength-splitting fiber coupler}
\threeDfig{3Db_fib_wdm}
\I  A fusion of result 9 (fiber coupler) and result 5 (wavelength splitter)
\I  Shows the power of full-parameter design-by-specification
\nextpage

@@

\oursection{Results summary}
\stepwise{
\I  Variety of devices suggests all devices possible
    \BI Converters: both TE and TM polarizations
    \I  Splitters: spatial, polarization, wavelength
    \I  Hubs: 3x3, 4x4, 2x2x2
    \I  Fiber couplers: compact, mode-splitting, wavelength-splitting \EI
\step{
\I  Design-by-specification is a key enabler
    \BI All 11 final results achieved in only 3 weeks
    \I  Of course, 7 years of development and 18 months of programming\ldots \EI
}
\step{
\I  Individual design runtimes between 8-80 hours
    \BI Many future speedups possible at all levels \EI
}}

@@

\oursection{Conclusion}
\footnotetext{$^\ast$maybe}
\I  How to design any$^\ast$ linear multi-mode nanophotonic device
    \BI using the full parameter space
    \I  simply by describing its operation \EI
\pause
\I  Our method results in designs which are
    \BI extremely compact
    \I  manufacturable \EI
\pause
\I  Devices can be designed which are robust to
    \BI wavelength and temperature shifts 
    \I  fabrication error \EI
\EI
\end{document}
